\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoTitleTopPadding}[1]{\vspace{0.5pt} \item\small #1 \vspace{-2pt}}
\newcommand{\resumeItemNoTitle}[1]{\item\small #1 \vspace{-2pt}}

\newcommand{\resumeSubheadingExtra}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{5pt}
    \small #5 \vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingNoBullet}[4]{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeAdditionalInfo}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{-}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ganesh Ravichandran} & \textit{Authorized to work in the US for any employer}\\
  \href{https://thebatmanofbutler.github.io}{https://thebatmanofbutler.github.io} & Email : \href{mailto:the.ganesh.ravichandran@gmail.com}{the.ganesh.ravichandran@gmail.com}\\
   & Mobile : 516-382-2920 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart


    \resumeSubheading
      {SOOT (Seed Startup, AI copilot for visual media)}{New York, NY}
      {Senior Software Engineer}{Feb. 2021 - Oct. 2024}
      \resumeItemListStart
        \resumeItemNoTitle {\textit{Developed critical upload and security infrastructure}}
        \resumeItemListStart
          \resumeItemNoTitle {Built foundational upload pipeline leveraging CLIP for embedding generation, UMAP for dimensionality reduction, and FAISS for similarity search. Powered \textbf{100\% of user content integration} into the platform.}
          \resumeItemNoTitle {Architected Lambda@Edge-based secure file-serving infrastructure that was integrated with S3 and API authorization, \textbf{significantly improving user file security}.}
          \resumeItemNoTitle {Implemented and maintained Firebase Authentication across the stack, integrating Google SSO, password recovery, and secure API authorization.}
          \resumeItemNoTitle {Extended GraphQL API functionality to support comprehensive queries, enabling users to download entire spaces or account data seamlessly. This was \textbf{requested by 60\% of users}.}
        \end{itemize}
        \resumeItemNoTitleTopPadding {\textit{Identified and optimized infrastructure bottlenecks}}
        \resumeItemListStart
          \resumeItemNoTitle {Designed a custom horizontal autoscaler that adjusted Kubernetes worker pods based on SQS message queue size, enabling a \textbf{2x increase in user upload capacity}.}
          \resumeItemNoTitle {Implemented OpenTelemetry across all backend services and enabled distributed tracing via Zipkin, \textbf{reducing p0 incident response time by 30\%} on average.}
          \resumeItemNoTitle {Managed compute resources using Terraform to support product deployments and rollbacks. Automated deployment process across the stack, \textbf{decreasing deployment time by 20\%}.}
        \end{itemize}
        \resumeItemNoTitleTopPadding {\textit{Enhanced user experience and product growth}}
        \resumeItemListStart
          \resumeItemNoTitle {Built an Electron app that synced local files, driving a \textbf{70\% increase in file uploads} among beta testers.}
          \resumeItemNoTitle {Led development on \textit{Playgrounds}, fast-loading static snapshots of user spaces that accounted for \textbf{90\% of DAUs}.}
          \resumeItemNoTitle {Delivered an intuitive VueJS upload manager for streamlined file queuing and monitoring, improving user satisfaction and upload reliability}
        \end{itemize}
        \resumeItemNoTitleTopPadding {\textit{Defined company culture as founding engineer}}
        \resumeItemListStart
          \resumeItemNoTitle {Advocated for a shift from research-focused work to a data-driven GTM product strategy, \textbf{enabling a beta launch in 5 weeks}.}
          \resumeItemNoTitle {Mentored new grad across the entire stack, \textbf{freeing up 70\% of the manager's time} for other priorities.}
          \resumeItemNoTitle {Instituted a two-week feature freeze to clear tech debt as triage engineer, \textbf{cutting p0 issues by 40\%} for months.}
        \end{itemize}
      \resumeListEnd  

    \resumeSubheading
      {LiveStories (Series A Startup, focused on civic data storytelling)}{Seattle, WA}
      {Software Engineer (Technical Lead on \textup{LiveData})}{Sep. 2019 - Feb. 2021}
      \resumeItemListStart
        \resumeItemNoTitle {\textit{LiveData} (Latest version of flagship product, an  online data explorer and chart builder for proprietary civic data)}
        \resumeItemListStart
          \resumeItemNoTitle {\textbf{Managed three engineers} across three continents to develop and launch an MVP to replace existing app}
          \resumeItemNoTitle{\textbf{Advised CEO} on design/development strategy and \textbf{cut sprint planning meeting lengths in half}}
          \resumeItemNoTitle {Developed \textbf{4/7 of the MVP's critical features}, including authentication, location-based search, and chart editing} \resumeItemNoTitle {Re-architected the search function for the data library and \textbf{reduced load time by 40\%}}
          \resumeItemNoTitle {Facilitated transition for existing users by integrating LiveData into the current product UX}
        \end{itemize}
        \resumeItemNoTitleTopPadding {\textit{Forward} (Platform for local governments to provide COVID-19 economic relief to small businesses)}
        \resumeItemListStart
          \resumeItemNoTitle {Shipped an email campaign launch platform for government clients to reach businesses based on their eligibility for a given aid program, \textbf{used by more than half of our clients}}
          \resumeItemNoTitle {Built tabular React UIs for government clients to analyze aid eligibility for \textbf{over 10,000 businesses}} \resumeItemNoTitle {Developed and maintained UIs to empower struggling businesses to apply to \textbf{more than 130 municipal and federal aid programs} and gain access to \textbf{over \$600,000 in available pandemic relief}}
        \end{itemize}
      \resumeListEnd


  \resumeListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingExtra
      {Columbia University}{New York, NY}
      {Bachelor of Arts in Computer Science}{Sept. 2014 -- Feb. 2018}
    \resumeListEnd

% --------TECHNICAL SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Proficient}
      {TypeScript/JavaScript (React, Vue, Node), Python (Flask, NumPy), Terraform, MongoDB, AWS (EC2, DynamoDB, S3, EKS, Cloudfront), Linux, GraphQL
    \resumeSubItem{Familiar}
      {C, C++, Go, Kubernetes, Docker}}
 \resumeListEnd


%-------------------------------------------
\end{document}
